An Extensible Approach to Verification of Embedded Network Systems*

### 2014-04-25 tech-project/implementation.tex
changes

% general flow Each of these calls are received in the translator in the order in which they are visited within the tree. It is up to the client (in this case, the author of the C-translator) to decide which of these methods they wish to override and perform custom actions within.

%\subsubsection{Translation output}
%Output of translated code is done using \textit{Stringtemplate} -- a third-party tool written in Java that allows users to define parameterizable templates. Like the name suggests, a template is simply ``a document with holes" that the user choses when and how to fill.

%An example C function definition template is shown below.

%\begin{verbatim}
%function_def(modifier, type, name, params, 
%                               vars, stmts) ::= <<
%<modifier> <type> <name> (<params; sep = ", ">) {
%    <vars; sep = "\n">
%    <stmts; sep = "\n">
%}>>
%\end{verbatim}

%User supplied attributes, enclosed in \texttt{<..>}, indicates the position of that attribute relative to others. It is entirely up to the user to define which attributes to fill in, and how complex they want them to be. For example, the user might choose to fill the \texttt{params} attribute with a simple string, or a separately defined \texttt{parameter} template, which in turn might use another separately defined \texttt{type} template.

%\begin{verbatim}
%parameter(type, name) ::= "<type> <name>"
%\end{verbatim}

%In the context of language translation, these templates, when stored on a stack and manipulated over the course of the aforementioned AST traversal, help simplify the task of producing complicated, structured blocks of C output. For instance, upon visiting \texttt{preOperationDec}, a \texttt{function\_def} template can be instantiated by the client and pushed onto a global translation stack with its \texttt{name}, return \texttt{type}, and \texttt{modifier} attributes filled in. As \texttt{preOperationDec}'s children are visited, the \texttt{function\_def} template currently at the top of the stack receives similarly constructed parameter, variable, and statement templates from the nodes being walked. Upon reaching \texttt{postOperationDec}, we can be assured that the function has been completely filled in with the appropriate templates -- assuming the user has implemented the children's visit methods.

%Hence, the only actual work being performed within visit methods is forwarding appropriate information from tree-node it represents, to an externally defined template. This allows us to exploit (in shameless design pattern parlance) a strict model view controller (MVC) separation in the translator's codebase between the mechanism that does the AST visiting (controller), the tree nodes from which we're adding information to templates (model), and the external file containing all available C language templates (view).

@@

In spite of this, our reasoning for choosing to pursue dynamic allocation over static, rests in the language itself. Being a language that relies heavily on the notion of formally specified objects (components), everything in RESOLVE from the `primitive' types such as booleans and integers, to the more complicated (user defined) ones such as Stacks and Queues, are modeled, specified, and implemented in the same way: Using the standard RESOLVE machinery discussed in Section \ref{sec:specifiying}.

>>>>

@@

In spite of this, our reasoning for choosing to pursue dynamic allocation over static, rests in the language itself. Being a language that relies heavily on the notion of formally specified objects (components), everything in RESOLVE from the `primitive' types such as booleans and integers, to the more complicated ones such as Stacks and Queues, are modeled, specified, and implemented in the same way: Using the standard RESOLVE machinery discussed in Section \ref{sec:specifiying}.

### 2014-04-25 tech-project/led_trans.tex
changes

\begin{figure}
\centering
\begin{verbatim}
/*
 * Generated by the RESOLVE to C translator. 
 * This file should not be modified.
 */
#ifndef __LEDS_TEST_H
#define __LEDS_TEST_H

#include ".../RESOLVE.h"
#include ".../Facilities/.../Std_Boolean_Fac.h"
#include ".../Facilities/.../Std_Integer_Fac.h"
#include ".../Facilities/.../Std_Clock_Fac.h"
#include ".../Concepts/.../Leds_Template.h"
#include ".../Concepts/.../Std_Leds_Realiz.h"
#include ".../Concepts/.../Toggling_Realiz.h"

typedef struct Led_Facility Led_Facility;
struct Led_Facility {
    Leds_Template* core;
    Toggling_Capability_for_Leds_Template* 
                      Toggling_Capability;
};
Led_Facility Led_Facility_Var;
void Leds_Test_create();
void Leds_Test_destroy();

#endif
\end{verbatim}
\caption{LED\_Demo.h}
\end{figure}

\begin{figure}
\centering
\begin{verbatim}
/*
 * Generated by the RESOLVE to C translator. 
 * This file should not be modified.
 */
#include "Leds_Test.h"
void Leds_Test_create() {
  Std_Boolean_Fac_create();
  Std_Integer_Fac_create();
  Std_Clock_Fac_create();
  r_type_ptr __arg_0 = Std_Integer_Fac_Var.core->
  createFromInteger(4, Std_Integer_Fac_Var.core->Integer);
  Led_Facility_Var.core = 
  new_Std_Leds_Realiz_for_Leds_Template(__arg_0);
  Led_Facility_Var.Toggling_Capability = 
  new_Toggling_Realiz_for_Toggling_Capability_of_LED_Template(
								      Led_Facility_Var.core);
  Std_Integer_Fac_Var.core->Integer->
  destroy(__arg_0, Std_Integer_Fac_Var.core->Integer);
}

void Leds_Test_destroy() {
    free_Std_Leds_Realiz_for_Leds_Template(
    				    Led_Facility_Var.core);
    Std_Boolean_Fac_destroy();
    Std_Integer_Fac_destroy();
}
\end{verbatim}
\caption{LED\_Test.c}
\end{figure}

>>>>

\begin{figure*}
\begin{minipage}{0.4\textwidth}
\begin{verbatim}
/*
 * Generated by the RESOLVE to C translator. 
 * This file should not be modified.
 */
#ifndef __LED_TELOS_DEMO_H
#define __LED_TELOS_DEMO_H

#include ".../RESOLVE.h"
#include ".../Facilities/.../Std_Bool_Fac.h"
#include ".../Facilities/.../Std_Int_Fac.h"
#include ".../Facilities/.../Std_Clock_Fac.h"
#include ".../Concepts/.../LED_Template.h"
#include ".../Concepts/.../Std_LED_Realiz.h"
#include ".../Concepts/.../Toggling_Realiz.h"

typedef struct LED_Facility LED_Facility;
struct LED_Facility {
    LED_Template* core;
    Toggling_Capability_for_LED_Template* 
                      Toggling_Capability;
};
LED_Facility LED_Fac_Var;

void LED_Telos_Demo_create();
void LED_Telos_Demo_destroy();
#endif
\end{verbatim}
\end{minipage}
\hspace{1.5cm} 
\begin{minipage}{0.4\textwidth}
\begin{verbatim}
/*
 * Generated by the RESOLVE to C translator. 
 * This file should not be modified.
 */
#include "LED_Telos_Demo.h"

void LED_Telos_Demo_create() {
  Std_Bool_Fac_create();
  Std_Int_Fac_create();
  Std_Clock_Fac_create();
  r_type_ptr __arg_0 = Std_Int_Fac_Var.core->
    createFromInt(4, Std_Int_Fac_Var.core->Integer);
  LED_Fac_Var.core = 
    new_Std_LED_Realiz_for_LED_Template(__arg_0);
  LED_Fac_Var.Toggling_Capability = 
    new_Toggling_Realiz_for_
    Toggling_Capability_of_LED_
    Template(LED_Fac_Var.core);
  Std_Int_Fac_Var.core->Integer->
    destroy(__arg_0, Std_Int_Fac_Var.core->Integer);
}

void LED_Telos_Demo_destroy() {
    free_Std_LED_Realiz_for_LED_Template(
    				    LED_Fac_Var.core);
    Std_Bool_Fac_destroy();
    Std_Int_Fac_destroy();
}
        ...
\end{verbatim}
\end{minipage}
\end{figure*}
